Summary Tables

### 2021-08-09 summary_tables.Rmd
Adding health outcomes to summary_tables markdown

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
})

@@

@@

# **2nd option**

>>>>

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
})

@@

## Duration tables

Case study specific duration tables for baseline and five scenarios (per day in km)

@@

## Health outcomes

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('ap',as.character(x))))
pa_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths),function(x)grepl('pa',as.character(x))))

sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}

scen_names <- rownames(scen_prop)

#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = 5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs per 100,000 {#change_YLL_age_100k}
```{r scen_prop = "asis"}
pop_by_age <- lapply(io[-2], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],5,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = 5)*100000
        )
  )

names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

YLLs per 100,000 people by gender by age group scenario

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2 + y, ncol(xx), by = 5)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,1:2], 1,
                          function(z)paste0(z[1], '_', z[2]))
  colnames(temp) <- scen_names
  temp
})

yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,5,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = 5) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:5, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5, function(y){
    xxx <- rowSums(xx[, pa_cols[seq(y, length(pa_cols), by = 5)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})

sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y) {
    xxx <- rowSums(xx[, ap_cols[seq(y, length(ap_cols), by = 5)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = 5) * 100000)
  )

names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")
```

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], 5, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = 5) * 100000))

names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities, function(x)
  rbind(
    ap_totals[[x]] / t(repmat(pop_by_age[[x]], 5 ,1)) * 100000,
    Total = colSums(ap_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                          length = 5) * 100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

## BY DISEASE
Change in deaths total (for the city based on real population size) by scenario

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

Change in deaths per 100,000 people by scenario

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = 5)*100000))

names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

Change in YLL total (for the city based on real population size) by scenario

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = 5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                               length = 5) * 100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```

<!-- #------------------------------------------------------------------------------ -->
# **2nd option**
